---
title: "Posit Connect demo content at a glance"
output: 
  html_document:
    theme:
      bg: "#FFFFFF"
      fg: "#22333B" 
      primary: "#297075"
      dark: "#213D4F"
      light: "#A2B8CB"
      base_font: "Lato, sans-serif"
      heading_font: "Lato, sans-serif"
      border-color: "#419599"
      gray-100: "#949494"

---


```{r setup, include=FALSE}
library(connectwidgets)
library(dplyr)
library(lubridate)

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

client <- connect(
  # server  = Sys.getenv("CONNECT_SERVER"),
  # api_key = Sys.getenv("CONNECT_API_KEY")
  )

# get that content
all_content <- client %>%
  content() %>% 
  #creating year variables to easily filter to more recent content
  mutate(created_year = year(created_time),
         updated_year = year(updated_time))

```

Welcome to the Customer Success demo content landing page. Use this to find examples of deployed content on Connect that you can share with customers. And use this landing page to demo how helpful connectwidgets can be to point a team to the content they need to see.

## Applications {.tabset .tabset-fade .tabset-pills}

### Shiny

```{r}
all_content %>% 
  #we need to figure out meaningful tagging or just rely on specific pieces of content and surface them individually.
  filter(grepl("shiny", name) & !grepl("python", name), created_year >= 2021) %>% 
  # count()
  rsc_grid()
```

### Shiny for Python

```{r}
all_content %>% 
  filter(grepl("shiny", name) & grepl("python", name), created_year >= 2021) %>% 
  # count()
  rsc_grid()
```

### Dash

```{r}
all_content %>% 
  by_tag("Dash") %>% 
  filter(created_year >= 2021) %>% 
  rsc_grid()
```

### Streamlit

```{r}
all_content %>% 
  # by_tag("Streamlit") %>% 
  # would ideally like to do this by tag but only one streamlit app on colorado has the streamlit tag today - let's discuss tags when we meet
  filter(grepl("streamlit", name), created_year >= 2021) %>% 
  rsc_grid()
```

### Bokeh

```{r}
all_content %>% 
  # by_tag("Bokeh") %>% 
  filter(grepl("bokeh", name), created_year >= 2021) %>% 
  rsc_grid()
```

## Documents {.tabset .tabset-fade .tabset-pills}

### R Markdown

```{r}
all_content %>% 
  # ideally by a tag 
  filter(grepl("rmd", name), !grepl("parameterized", name), created_year >= 2021) %>% 
  rsc_grid()
```

### Parameterized Rmd

```{r}
all_content %>% 
  # ideally by a tag 
  filter(grepl("parameterized", name), created_year >= 2021) %>% 
  rsc_grid()
```

### Interactive documents

```{r}
all_content %>% 
  # ideally by a tag but there are probably some other methods to dig up these examples
  filter((grepl("interactive", name) & grepl("document", name)) | 
           (grepl("shiny", name) & grepl("document", name)), 
         created_year >= 2021) %>% 
  rsc_grid()
```

### Quarto

```{r}
all_content %>% 
  filter(grepl("quarto", name), created_year >= 2021) %>% 
  rsc_grid()
```

### Jupyter Notebook

```{r}
all_content %>% 
  filter(grepl("jupyter", name) & grepl("notebook", name), created_year >= 2021) %>% 
  # count()
  rsc_grid()
```

### connectwidgets

You're lookin' at it.

```{r echo=FALSE}
# all_content %>%
#   filter(grepl("connectwidgets", name), created_year >= 2021) %>%
#   #no clue why this is working as a table but not as a grid...
#   rsc_table()
```


## APIs
```{r}
all_content %>% 
  filter(content_category == "api", created_year >= 2021) %>% 
  rsc_grid()
```

## Pins

Python pins now included.
```{r}
all_content %>% 
  filter(content_category == "pin", created_year >= 2021) %>% 
  rsc_grid()
```
