---
title: "Posit Connect Display Case"
output: 
  html_document:
    theme:
      bg: "#FFFFFF"
      fg: "#22333B" 
      primary: "#297075"
      dark: "#213D4F"
      light: "#A2B8CB"
      base_font: "Lato, sans-serif"
      heading_font: "Lato, sans-serif"
      border-color: "#419599"
      gray-100: "#949494"

---


```{r setup, include=FALSE}
library(connectwidgets)
library(dplyr)
library(lubridate)

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

client <- connect(
  server  = Sys.getenv("CONNECT_SERVER"),
  api_key = Sys.getenv("CONNECT_API_KEY")
  )

# get that content
all_content <- client %>%
  content() %>% 
  #creating year variables to easily filter to more recent content
  mutate(created_year = year(created_time),
         updated_year = year(updated_time))

cs_demo_content <- all_content %>% 
  by_tag("cs_demo")
# eventually this will be by display_case
```

Welcome to the Customer Success demo content landing page. Use this to find examples of deployed content on Connect that you can show your customers. And use this landing page to demo how helpful connectwidgets can be to point a team to the content they need to see.

## Applications {.tabset .tabset-fade .tabset-pills}

### Shiny

```{r}
# all_content %>% 
#   #we need to figure out meaningful tagging or just rely on specific pieces of content and surface them individually.
#   filter(grepl("shiny", name) & !grepl("python", name), created_year >= 2021) %>% 
#   # count()
#   rsc_grid()

cs_demo_content %>% 
  by_tag("r_shiny") %>% 
  rsc_grid()
```

### Shiny for Python

```{r}
all_content %>%
  filter(grepl("shiny", name) & grepl("python", name), created_year >= 2021) %>%
  # count()
  rsc_grid()

# cs_demo_content %>% 
#   by_tag("python_shiny")
```

### Dash

```{r}
# all_content %>% 
#   by_tag("Dash") %>% 
#   filter(created_year >= 2021) %>% 
#   rsc_grid()

cs_demo_content %>% 
  by_tag("dash") %>% 
  rsc_grid()
```

### Streamlit

```{r}
# all_content %>% 
#   # by_tag("Streamlit") %>% 
#   # would ideally like to do this by tag but only one streamlit app on colorado has the streamlit tag today - let's discuss tags when we meet
#   filter(grepl("streamlit", name), created_year >= 2021) %>% 
#   rsc_grid()

cs_demo_content %>% 
  by_tag("streamlit") %>% 
  rsc_grid()
```

### Bokeh

```{r}
# this needs to be redone when we have any bokeh apps tagged
all_content %>%
  # by_tag("Bokeh") %>%
  filter(grepl("bokeh", name), created_year >= 2021) %>%
  rsc_grid()

# cs_demo_content %>% 
#   by_tag("bokeh") %>% 
#   rsc_grid()
# nothing here yet

# all_content %>% 
#   by_tag("bokeh") %>% 
#   rsc_grid()
#nothing
```

## Documents {.tabset .tabset-fade .tabset-pills}

### R Markdown

```{r}
# all_content %>% 
#   # ideally by a tag 
#   filter(grepl("rmd", name), !grepl("parameterized", name), created_year >= 2021) %>% 
#   rsc_grid()

cs_demo_content %>%
  by_tag("r_markdown") %>%
  rsc_grid()
```

### Parameterized Rmd

```{r}
# all_content %>% 
#   # ideally by a tag 
#   filter(grepl("parameterized", name), created_year >= 2021) %>% 
#   rsc_grid()

cs_demo_content %>%
  by_tag("parameterized") %>%
  rsc_grid()
```

### Interactive documents

```{r}
# all_content %>% 
#   # ideally by a tag but there are probably some other methods to dig up these examples
#   filter((grepl("interactive", name) & grepl("document", name)) | 
#            (grepl("shiny", name) & grepl("document", name)), 
#          created_year >= 2021) %>% 
#   rsc_grid()

cs_demo_content %>%
  by_tag("interactive_docs") %>%
  rsc_grid()
```

### Quarto

```{r}
# all_content %>% 
#   filter(grepl("quarto", name), created_year >= 2021) %>% 
#   rsc_grid()

# note needed to use all_content here
cs_demo_content %>%
  by_tag("quarto") %>%
  # rsc_grid()
  rsc_table()
#this will display as a table but not a grid
```

### Jupyter Notebook

```{r}
# all_content %>% 
#   filter(grepl("jupyter", name) & grepl("notebook", name), created_year >= 2021) %>% 
#   # count()
#   rsc_grid()

#note needed to use all_content here
all_content %>%
  by_tag("jupyter") %>%
  rsc_grid()
```

### connectwidgets

You're lookin' at it.

```{r echo=FALSE}
# all_content %>%
#   filter(grepl("connectwidgets", name), created_year >= 2021) %>%
#   #no clue why this is working as a table but not as a grid...
#   rsc_table()
```


## APIs {.tabset .tabset-fade .tabset-pills}

### Plumber
```{r}
# all_content %>% 
#   filter(content_category == "api", created_year >= 2021) %>% 
#   rsc_grid()

all_content %>%
  by_tag("plumber") %>%
  rsc_grid()
```

### Tableau Extensions
```{r}
cs_demo_content %>%
  by_tag("tableau_extensions") %>%
  rsc_grid()
```


### Flask

```{r}
cs_demo_content %>%
  by_tag("flask") %>%
  rsc_grid()
```

### Fast API

```{r}
cs_demo_content %>%
  by_tag("fast_api") %>%
  rsc_grid()
```

## Pins

Python pins now included.
```{r}
# all_content %>% 
#   filter(content_category == "pin", created_year >= 2021) %>% 
#   rsc_grid()

cs_demo_content %>%
  by_tag("pins") %>%
  rsc_grid()
```
